### 2014-02-27 paper/tubes.tex
update of algorithm text

We created a tool which novice designers can use to create tube-powered interfaces in arbitrary 3D models.  This tool allows users to brush over the surface of their model to either select exterior connection points of their tubes (see Figure \ref{fig:tool-process-interior}) or to author the tubes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the user's selections are made, our tool creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).  The resultant routing is subtracted from the user's mesh.  The modified mesh can then be 3D printed.

@@

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This figure has several sub-figures.  a) shows a model with path shape and exterior connection point(s) brushed.  b) highlights the points which can't be tubed as drawn (if they are not connected, too tight, etc.).  c) shows our physics-based, energy-minimizing rod/tube and any path-smoothing that we do, d) shows the printed object with the tube (with something in it, EL wire presumably)}
\label{fig:tool-process-interior}
\end{figure}

@@

Our problem here is a relaxed version of the Chinese Postman Problem$^{[\valkyrie{citation needed}]}$ in which we wish to traverse all edges of the graph described in the user's input (as the edges of the graph are the lines the user wishes to have lit) with a single circuit.  It is a relaxation in that we allow the creation of non-existing paths: if components are disconnected (e.g., a user wishes to spell ``UIST" in neon lights), we must create edges that connect them; additionally we can create edges to connect odd-degree vertices rather than simply retracing existing edges.  In the final design, all created edges will be shielded by dark material so the inserted medium is not visible.

We want a semi-Eulerian graph (i.e., we want a graph in which every vertex but two have even degree) so that the desired medium can be inserted, traverse every edge, and exit the graph at a different vertex.

Let $G=(V,E_0)$ s.t. $\forall e \in E_0, weight(e)=0, start \in V $ the start point $end \in V$ the end point.  Let $e_{temp} = (start, end)$, $E' = e_{temp} \cup E$.

@@

At this stage, we want an Eulerian graph: i.e., we need every vertex to be of even degree.  Let $V_{odd} = \{ v \in V s.t. degree(v) \% 2 = 1 \}$.  Create $E_{circuit} = V_{odd} \times V_{odd}$, s.t. $\forall e=(u,v) \in E_{circuit}, weight(e) = distance(u, v)$.  Find minimum matching $E_{circuit-min} \subseteq E_{circuit}$.  Let $E' = (E\setminus e_{temp}) \cup E_{circuit-min}$.

@@

>>>>

We created a tool which novice designers can use to create tube-powered interfaces in arbitrary 3D models.  This tool allows users to brush over the surface of their model to either select exterior connection points of their tubes (see Figure \ref{fig:tool-process-interior}) or to author the tubes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the user's selections are made, we create a complete routing using either the exterior connection point method (A*) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing and use a physics-based rod simulation to minimize bending energy of tubes.  We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect).  The resultant routing is subtracted from the user's mesh.  The modified mesh can then be 3D printed.

@@

our tool creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

@@

@@

 (as the edges of the graph are the lines the user wishes to have lit)

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This figure has several sub-figures.  a) shows an SVG file with some line art  b) highlights the points which can't be tubed as drawn (if they are not connected, of odd degree, etc.).  c) shows our connected graph, d) shows our routing e) shows a printed thing with that kind of tube filled with EL wire}
\label{fig:tool-process-interior}
\end{figure}

This is a relaxed version of the Chinese Postman Problem\footnote{\url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create edges to connect odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be shielded by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).

We want a semi-Eulerian graph (i.e., we want a graph in which every vertex but two have even degree) so that the desired medium can be inserted, traverse every edge, and exit the graph at a different vertex.  Let $G=(V,E_0)$ s.t. $\forall e \in E_0, weight(e)=0, start \in V $ the start point $end \in V$ the end point.  Let $e_{temp} = (start, end)$, $E' = E + e_{temp}$.

@@

At this stage, we want an Eulerian graph: i.e., we need every vertex to be of even degree.  Let $V_{odd} = \{ v \in V s.t. degree(v) \% 2 = 1 \}$.  Create $E_{circuit} = V_{odd} \times V_{odd}$, s.t. $\forall e=(u,v) \in E_{circuit}, weight(e) = distance(u, v)$.  Find minimum matching $E_{circuit-min} \subseteq E_{circuit}$.  Let $E' = E \cup E_{circuit-min}$.

Now to remove our temporary edge and make the graph semi-Eulerian instead of Eulerian, let $E' = E' \setminus e_{temp}$.

@@

We believe that a lower total weight matching is possible by connecting components and ensuring edge degree evenness together in a global process, however it this not crucial for our purposes.
